True versus apparent shapes of astrophysical bow shocks

### 2017-02-10 papers/Paper1/sec-conic.tex
Solved more mathematical inconsistencies in conics section

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization
\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
  projected shape are developed in appendix \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
-\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi &< t < \pi \\
R_0 &= a - x_0 \\
\end{align}
Where $a$ and $b$ are real, positive numbers.

@@

For the rest of the parameters, the equation for ellipses and hyperbolas are very similar, except for a sign in some terms. In all cases, the upper sign will
correspond to ellipses and the lower sign for hyperbolas:

\begin{align}
R_{90} = b\left[\pm \left(1-\left(a\mp R_0\right)^2\right)\right]^{1/2}\label{eq:conic-R90}
\end{align}

@@

Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x &= a\Cos(t)-x_0 \\ 
y &= b\Sin(t)\cos\phi \\
z &=  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
-\cot t ~\mathrm{if~ellipse} \\
\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

@@

\begin{align}
D' &= D\cos i \\
R'_0 &= a' - (a-R_0)\cos i \\
R'_0 &= \left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (a-R_0)\cos i
\end{align}

With  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\label{eq:qprime}
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$

The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
  \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
  \label{eq:Aprime}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$. 
% \begin{figure*}
% \includegraphics[width=0.8\linewidth]{conic2}
% \label{fig:conic2}
% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
% \end{figure*}

>>>>

Due to the similarities between the parametrization of the ellipse and the hyperbola, we can do the following parametrization, using the convention
that if a dual sign appears, the upper sign correspond to the elliptical quadrics, and the lower sign to the hyperbolic quadrics
\footnote{Equations (\ref{eq:par-x}) to (\ref{eq:b-prime}) does not apply for paraboloids. Instead, the parametrization and the
  projected shape are developed in appendix \ref{app:parabola}}:
\begin{align}
x &= a\Cos(t)-x_0 \label{eq:par-x}\\ 
y &= b\Sin(t) \label{eq:par-y}
\end{align}
where:
\begin{align}
\Cos(t) &= \left\lbrace \begin{array}{c}
\cos t ~\mathrm{if~ellipse} \\
-\cosh t ~\mathrm{if~hyperbola}
\end{array}\right.\\
\Sin(t) &= \left\lbrace \begin{array}{c}
\sin t ~\mathrm{if~ellipse} \\
\sinh t ~\mathrm{if~hyperbola}
\end{array}\right. \\
-\pi &< t < \pi \\
x_0 &= \pm a - R_0 \label{eq:x0}\\
\end{align}
Where $a$ and $b$ are real, positive numbers.

@@

For the rest of the parameters, the equation for ellipses and hyperbolas are very similar:

\begin{align}
R_{90} = b\left[\pm \left(1-\frac{x_0^2}{a^2}\right)\right]^{1/2}\label{eq:conic-R90}
\end{align}

@@

Once the parametrization is done, we can find the apparent shape of
the shell in the observer's frame, following the procedure explained
in section \ref{sec:projection}.  First of all, the intrinsic 3D shape of the shell is given by:
\begin{align}
x &= a\Cos(t)-x_0 \\ 
y &= b\Sin(t)\cos\phi \\
z &=  b\Sin(t)\sin\phi
\end{align}
The azimutal angle where the line of sight is tangent to the shell is given by equation (\ref{eq:tanphi}) and (\ref{eq:alpha}), then:
\begin{align}
\sin\phi_t &= \frac{b}{a}\tan i\Cot(t) 
\end{align}
where:
\begin{align}
\Cot(t) = \left\lbrace \begin{array}{c}
\cot t ~\mathrm{if~ellipse} \\
\coth t ~\mathrm{if~hyperbola}
\end{array}\right.
\end{align}

@@

Finally, using $D' = D\cos i$ and substituting $a'$ instead of $a$ in equation (\ref{eq:x0}) we find that:

\begin{align}
R'_0 &= \pm a' - x_0\cos i \\
R'_0 &= \pm\left(a^2\cos^2 i \pm b^2\sin^2 i\right)^{1/2}  - (\pm a-R_0)\cos i
\end{align}

Defining  $f(i;\theta_c)\equiv\left(1\pm\tan^2\theta_c\tan^2i\right)^{1/2}$ we find that:
\begin{align}
\frac{R'_0}{D'}=\frac{R_0}{D}\left(1\pm A\cot^2\theta_c(f(i;\theta_c)-1) \right)
\label{eq:qprime}
\end{align}
%Where $A\equiv \frac{R_c}{R_0}$
The Radius of curvature in the observer's frame is given by $R'_c=\frac{b'^2}{a'}$. Then:
\begin{align}
A'\equiv  \frac{R'_c}{R'_0} = \frac{A}{\cos^2 i f(i;\theta_c)\frac{q'}{q}}
  \label{eq:Aprime}
\end{align}
where $q=\frac{R_0}{D}$ and $q' = \frac{R'_0}{D'}$. 
% \begin{figure*}
% \includegraphics[width=0.8\linewidth]{conic2}
% \label{fig:conic2}
% \caption{Graphic example of the increasing of the projected radius of curvature with inclination}
% \end{figure*}
